Predicting tree failure likelihood for utility risk mitigation via a novel convolutional neural network

### 2021-02-15 docs/manuscript/manuscript.tex

\documentclass[Journal,letterpaper, SingleSpace]{ascelike-new}
%\usepackage{etex}
%\newcommand{\num}{6{} }

@@

\subsection{Hyperparameter optimization}
We used the Hyperband approach \cite{li2018hyperband} to perform a grid search to find the optimal values of the following hyperparameters:
\begin{itemize}
    \item kernel size in first convolutional layer
    \item number of units in first densely connected layer
    \item dropout rate applied to outputs of first dense layer
    \item activation function for first dense layer
    \item number of units in second densely connected layer
    \item dropout rate applied to outputs of second dense layer
    \item activation function for second dense layer    
    \item learning rate (of Adam optimizer)
\end{itemize}

\section{Results}

>>>>

\documentclass[Journal,letterpaper, SingleSpace, InsideFigs]{ascelike-new}
%\usepackage{etex}
%\newcommand{\num}{6{} }

@@

\subsection{Hyperparameter optimization}
We used the Hyperband approach \cite{li2018hyperband} to perform a grid search to find the optimal values of the following hyperparameters:
\begin{itemize}
    \item kernel size in first convolutional layer $ks$
    \item number of units in first densely connected layer $u_1$
    \item dropout rate applied to outputs of first dense layer $d_1$
    \item activation function for first dense layer $a_1$
    \item number of units in second densely connected layer $u_2$
    \item dropout rate applied to outputs of second dense layer $d_2$
    \item activation function for second dense layer $a_2$
    \item learning rate (of Adam optimizer) $\lambda$
\end{itemize}

\begin{table}[h!]\small
    \centering
    \begin{tabular}{|l | l l l l| l l l l| l l l l | l l l l|}\hline
    %\bf Scenario 
        &  \multicolumn{4}{c|}{\texttt{Pr\_Po\_Im}} 
            & \multicolumn{4}{c|}{\texttt{Pr\_Im}} 
                &  \multicolumn{4}{c|}{\texttt{PrPo\_Im}} 
                    &  \multicolumn{4}{c|}{\texttt{Pr\_PoIm}}  \\\hline
    %\bf Resolution
        & 64 & 128 & 224 & 384 
            & 64 & 128 & 224 & 384 
                & 64 & 128 & 224 & 384
                    & 64 & 128 & 224 & 384  \\\hline
    %\bf Hyperparameter 
    $ks$    &  &  &  &  &   &  &  &  &   &  &  &  &   &  &  &   \\
    $u_1$   &  &  &  &  &   &  &  &  &   &  &  &  &   &  &  &   \\
    $d_1$   &  &  &  &  &   &  &  &  &   &  &  &  &   &  &  &   \\
    $a_1$   & ReLu  &  &  &  &   &  &  &  &   &  &  &  &   &  &  &   \\
    $u_2$   &  &  &  &  &   &  &  &  &   &  &  &  &   &  &  &   \\ 
    $d_2$   &  &  &  &  &   &  &  &  &   &  &  &  &   &  &  &   \\
    $a_2$   & ReLu &  &  &  &   &  &  &  &   &  &  &  &   &  &  &   \\
    $\lambda$  
            &  &  &  &  &   &  &  &  &   &  &  &  &   &  &  &   \\\hline
    \end{tabular}
    \caption{Optimal hyperparameters found using the Hyperband search algorithm for all classification scenario and input image resolution combinations.}
    \label{tab:opt-hyp}
\end{table}
\section{Results}
